Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-30 research_proposal/research_proposal_draft.qmd
add algorithm in appendix

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
format: 
  pdf:
    # include-in-header:
    #   text: |
    #     \usepackage{amsmath}
    #     \usepackage{mathspec}
    #     \newcommand{\b}[1]{\boldsymbol{#1}}
    mathspec: true
    number-sections: true
---

@@

On the other hand, the optimal threshold $\delta^*$ does not have a closed-form solution, and is typically obtained by executing a rolling-window cross-validation procedure. The idea is to, for each rolling-window set, loop through a range of threshold values, compute the corresponding $\hat{\lambda}(\delta)$ and $\hat{\boldsymbol{R}}^{N}_{1}$. Then we select the one that minimises the average out-of-sample reconciled forecast errors. Although it is not required to fit forecasting models multiple time, the cross-validation procedure is still computationally expensive as it computes the NOVELIST estimator and perform reconciliation for each threshold value. The formal algorithm is given in @pseudo_novelist_cv, in the Appendix section.

@@

## Appendix

Algorithm 1

>>>>

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        <!-- \newcommand{\b}[1]{\boldsymbol{#1}} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
    mathspec: true
    number-sections: true
---

@@

On the other hand, the optimal threshold $\delta^*$ does not have a closed-form solution, and is typically obtained by executing a rolling-window cross-validation procedure. The idea is to, for each rolling-window set, loop through a range of threshold values, compute the corresponding $\hat{\lambda}(\delta)$ and $\hat{\boldsymbol{R}}^{N}_{1}$. Then we select the one that minimises the average out-of-sample reconciled forecast errors. Although it is not required to fit forecasting models multiple time, the cross-validation procedure is still computationally expensive as it computes the NOVELIST estimator and perform reconciliation for each threshold value. The formal algorithm is given in @fig-novelist_cv, in the @sec-appendix Appendix.

@@

\pagebreak

## Appendix {#sec-appendix}

#### Algorithm: NOVELIST cross-validation for optimal threshold $\delta^*$ {-}

![NOVELIST cross-validation procedure](D:/Github/Recon_Honours_Thesis/research_proposal/figs/novelist_cv_algo.png){#fig-novelist_cv height=70%}

#### Data generating progress design {-}

<!-- ```{=latex} -->
<!-- \begin{algorithm} -->
<!-- \caption{Cross-validation procedure to select optimal threshold $\delta^*$ for NOVELIST} -->
<!-- \begin{algorithmic}[1] -->
<!-- \State \textbf{Input:} Residual matrix $E$ of dimension $T \times p$, grid of threshold candidates $\{\delta_j\}$, window size $n$ -->
<!-- \For{each threshold candidate $\delta_j$} -->
<!--     \For{$t = n+1$ to $T$} -->
<!--         \State Define in-sample window: $E_{1:n} = \{e_{t-n}, ..., e_{t-1}\}$ -->
<!--         \State Compute sample covariance $\hat{\Sigma}_t = \frac{1}{n} E_{1:n}^\top E_{1:n}$ -->
<!--         \State Compute thresholded covariance: $\hat{\Sigma}^{\text{thr}}_t = \text{Threshold}(\hat{\Sigma}_t, \delta_j)$ -->
<!--         \State Compute NOVELIST: $\hat{\Sigma}^{\text{nov}}_t = (1 - \lambda) \hat{\Sigma}_t + \lambda \hat{\Sigma}^{\text{thr}}_t$ -->
<!--         \State Compute inverse: $W_t = (\hat{\Sigma}^{\text{nov}}_t)^{-1}$ -->
<!--         \State Compute MinT reconciliation matrix: $P_t = (S^\top W_t S)^{-1} S^\top W_t$ -->
<!--         \State Compute forecast error: $e_t = y_t - S P_t \hat{y}_t$ -->
<!--     \EndFor -->
<!--     \State Compute total CV loss $L_j = \sum_t \|e_t\|^2$ -->
<!-- \EndFor -->
<!-- \State \textbf{Output:} $\delta^* = \arg\min_{\delta_j} L_j$ -->
<!-- \end{algorithmic} -->
<!-- \end{algorithm} -->
<!-- ``` -->
